### 2022-08-03 main/chapter_2ljets.tex
add unblinding pros

>>>>

Blindness to data is useful, but not necessary.
All that is necessary is that our predictions are independent of the data
they are supposed to predict.
Probabilistically, that independence makes our Poisson likelihood assignments
justifiable, and scientifically it allows our modelling to be useful if it
makes accurate predictions.
If one knows what the data are, then it takes utter honesty ---
Feynman's ``leaning over backwards''~\cite{feynman1974cargo} ---
to assign predictions as if the data were unknown.
Blindness is a useful and wilful ignorance that automatically implements this
honesty without this backbreaking work.

% pro
Naturally, \atlas\ has an unblinding procedure that requires committee
review and approval based on internal documentation.
In the \atlas\ SUSY world, searches are nominally performed blind to signal
regions.
Control and validation regions are consumed in the design and modelling of
signal regions, so need to be inspected.
Control and validation region data are inspected, but this is not a problem
since they should also have negligibly small yields (contaminations) from
interesting signal models.
With negligible signal contaminations, control and validation region data can
be consumed to constrain the background modelling in addition to all other that
on which the Standard Model stands, and without being influenced by the signal
models to be tested in signal regions.

The \atlas\ SUSY approval procedure~\cite{atlas_twiki_susyapprove}
requires various criteria including, and not limited to, that the search has:
\begin{itemize}
\item defined all control, validation and signal regions,
\item evaluated signal contaminations in control and validation,
\item estimated all regions' simulated backgrounds,
\item outlined procedures to estimate non-simulated (data-driven) backgrounds,
\item evaluated variations due to experimental uncertainties in all regions
according to recommended procedures,
\item stated clearly how all other (theoretical) uncertainties will be treated.
\end{itemize}
So many aspects must be finalized blind, and for those that are not
finalized blind must have procedures defined such that they are not
influenced by the signal region data.
Positively, disallowing dependence of procedures on signal region data
eliminates one major source of unblinding error,
and requiring knowledge of signal contaminations supports the use of control
and validation region data.

% con
\TODO{flaws in that procedure:
explicit allowance of data-driven methods using SR data,
questionable enforcement of the stated procedures
}
